---
title: "Where do the french place the south of France?"
format: html
editor: visual
execute:
  echo: false
  error: true
  warning: false
---

## How people perceive the South

To answer the question, we asked our dear friends from the CESAB to give us information on:

-   Their childhood town
-   The town where they currently live
-   Which town is the first to be considered in the south
-   Their chilliness (because why not?)

```{r}
library(targets)
tar_config_set(store = here::here("outputs", "pipeline"), 
               script = here::here("analyses", "pipeline.R"))
```

We then joined each town given as the south by our participants with their geographic coordinates (longitude and latitude). We applied a PCA on these geographic coordinates to group together similar answers and identify how people differ in placing the south of France.

```{r}
tar_load(pca_survey_graph)

pca_survey_graph
```

So far, we can see that "*Anonymous1*"'s answer differ greatly from the others, but it's hard to perceive much more from this plot. Let's see how it is on a map of France!

```{r}
tar_load(pca_map_survey)

pca_map_survey
```

If we compare everyone's answers to the frontier between the south and the rest of France defined by our meteo analysis (showed as a dashed line), We can see that some people chose cities really close to that frontier. But we can also see that a lot of people chose cities on the Mediterranean coast as the south! 